This page and the next page should be removed

### 2022-05-28 analysis/manuscript.Rmd
Update cluster image

```{r, clusters, include=TRUE}
read_csv(clusters_file, col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) %>%
  ggplot(aes(x = time, y = channel, fill = cl_index)) +
  facet_grid(~contrast) +
  geom_raster() +
  scale_fill_viridis_c()
ggsave("clusters.pdf")
```

>>>>

```{r, clusters, include=TRUE}
read_csv(clusters_file, col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> clusters

clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cl_index)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  scale_fill_viridis_c()

  # Extract significant positive- or negative-going clusters
  mutate(cl = case_when(
    p_val < .05 & t_obs < 0 ~ paste0("neg (p = ", p_val, ")"),
    p_val < .05 & t_obs > 0 ~ paste0("pos (p = ", p_val, ")"),
    TRUE ~ "n.s."
  ) %>%
    factor()) %>%
  # Plot cluster image
  ggplot(aes(x = time, y = channel, fill = cl)) +
  facet_grid(~contrast) +
  geom_raster()
  scale_fill_viridis_c()
ggsave("clusters.pdf")
```
